Converting LaTeX Legacy R Journal Articles into R Markdown Articles using texor and rebib

### 2023-09-09 texor.Rmd
More specific mention of algorithm2e graphics instead of algorithm in general.

### Algorithms as figures

Algorithms as figures are supported, and the following description will yield the result in Figure \@ref(fig:alghow).

@@

```html
<figure id="alg:how">
<img src="alghow.png" style="width:100.0%" />
<p>initialization</p>
<figcaption>Algorithm 1: How to write algorithms</figcaption>
</figure>
```

>>>>

### Algorithm2e graphics as figures

Algorithm2e graphics using the `algorithm2e` package in LaTeX  are supported, and the following description will yield the result in Figure \@ref(fig:alghow).

@@

```html
<figure id="alg:how">
<img src="alghow.png" style="width:100.0%" />

<figcaption>Algorithm 1: How to write algorithms</figcaption>
</figure>
```

### 2023-09-09 texor.tex
using one r chunk for figure
More specific mention of algorithm2e graphics instead of algorithm in general.

\caption{Workflow of the document conversion conducted by texor.}\label{fig:workflow1}
\end{figure}

@@

\hypertarget{algorithms-as-figures}{%
\subsubsection{Algorithms as figures}\label{algorithms-as-figures}}

Algorithms as figures are supported, and the following description will yield the result in Figure \ref{fig:alghow}.

@@

\begin{verbatim}
<figure id="alg:how">
<img src="alghow.png" style="width:100.0%" />
<p>initialization</p>
<figcaption>Algorithm 1: How to write algorithms</figcaption>
</figure>
\end{verbatim}

>>>>

\caption{Workflow of the document conversion conducted by texor.}\label{fig:workflow}
\end{figure}

@@

\hypertarget{algorithm2e-graphics-as-figures}{%
\subsubsection{Algorithm2e graphics as figures}\label{algorithm2e-graphics-as-figures}}

Algorithm2e graphics using the \texttt{algorithm2e} package in LaTeX are supported, and the following description will yield the result in Figure \ref{fig:alghow}.

@@

\begin{verbatim}
<figure id="alg:how">
<img src="alghow.png" style="width:100.0%" />

<figcaption>Algorithm 1: How to write algorithms</figcaption>
</figure>
\end{verbatim}
